Design and Implementation of Probabilistic Programming Language Anglican

### 2017-02-26 paper/paper.tex
made toggle parameterized again, it is 'make ifl or make full'

\newtoggle{full}
\input{toggle-ifl }

@@

%An implementation of Anglican must therefore address three issues:
%\begin{itemize}
%    \item the Clojure syntax to introduce probabilistic Anglican
%        code inside Clojure modules;
%    \item source-to-source transformation of Anglican programs
%        into Clojure, so that probabilistic execution becomes
%        possible;
%    \item algorithms which run Clojure code, obtained by
%        transforming Anglican programs, according to the
%        probabilistic operational semantics.
%\end{itemize}
%Execution of probabilistic programs by inference algorithms is
%different from execution of deterministic programs.  A
%probabilistic program is executed multiple times, often hundreds
%of thousands or even millions of times for a single inference
%task. Random choices may affect which parts of the program code
%are executed and how often. Many inference algorithms require
%re-running the program multiple times partially, from a certain
%point on.  Different executions may employ different random
%choices. However, for efficient inference a correspondence
%between random choices in different executions should be
%maintained. These are just some of the challenges which were
%faced and solved during development of Anglican.

>>>>

\newtoggle{full}
\input{toggle}

@@

\iftoggle{full}{%
An implementation of Anglican must therefore address three issues:
\begin{itemize}
    \item the Clojure syntax to introduce probabilistic Anglican
        code inside Clojure modules;
    \item source-to-source transformation of Anglican programs
        into Clojure, so that probabilistic execution becomes
        possible;
    \item algorithms which run Clojure code, obtained by
        transforming Anglican programs, according to the
        probabilistic operational semantics.
\end{itemize}
Execution of probabilistic programs by inference algorithms is
different from execution of deterministic programs.  A
probabilistic program is executed multiple times, often hundreds
of thousands or even millions of times for a single inference
task. Random choices may affect which parts of the program code
are executed and how often. Many inference algorithms require
re-running the program multiple times partially, from a certain
point on.  Different executions may employ different random
choices. However, for efficient inference a correspondence
between random choices in different executions should be
maintained. These are just some of the challenges which were
faced and solved during development of Anglican.
}{}%
